\mpc: the FML solution

### 2021-05-05 1-Main.tex
Updates from Overleaf

\newcommand{\noteSM}[1]{\todo[color=red!40, author=\textbf{Salvador}, inline, caption={}]{#1}}
\newcommand{\noteJC}[1]{\todo[color=blue!40, author=\textbf{JC}, inline, caption={}]{#1}}
\newcommand{\noteSylvain}[1]{\todo[color=green!40, author=\textbf{Sylvain}, inline, caption={}]{#1}}
\newcommand{\noteAntoine}[1]{\todo[color=yellow!40, author=\textbf{Antoine}, inline, caption={}]{#1}}

@@

\usepackage{amsmath,amssymb,mathtools}
\usepackage{algorithmic,algorithm}

@@

\begin{document}
\begin{article}{
\title{MULTI process challenge : the FML solution}

@@

%\author{Jean-Christophe Bach, Salvador Martinez, Antoine Beugnard}
%\address{IMT Atlantique}

@@

@@

\noteSM{teste}
\noteJC{test}
\noteSylvain{Test}
\noteAntoine{Test}

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio}

>>>>

\newcommand{\noteSM}[1]{\todo[color=red!40, author=\textbf{Salvador}, inline, caption={}]{#1}}
\newcommand{\noteJC}[1]{\todo[color=pink!40, author=\textbf{JC}, inline, caption={}]{#1}}
\newcommand{\noteSylvain}[1]{\todo[color=green!40, author=\textbf{Sylvain}, inline, caption={}]{#1}}
\newcommand{\noteAntoine}[1]{\todo[color=yellow!40, author=\textbf{Antoine}, inline, caption={}]{#1}}
\newcommand{\noteFabien}[1]{\todo[color=orange!40, author=\textbf{Fabiem}, inline, caption={}]{#1}}

\newcommand{\mpc}{MULTI process challenge\xspace}

@@

%\usepackage{amsmath,mathtools}%amssymb,
\usepackage{algorithmic,algorithm}

@@

\begin{document}
\begin{article}{
\title{\mpc: the FML solution}

@@

%\author{Jean-Christophe Bach, Salvador Martinez, Antoine Beugnard, Fabien Dagnat}
%\address{IMT Atlantique}

@@

\author{Fabien Dagnat}
\address[b]{}

@@

\noteSM{test}
\noteJC{test}
\noteSylvain{Test}
\noteAntoine{Test}
\noteFabien{test}

@@

%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
%\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio}

% à utiliser d'après le style (avec biber), voir comment ça fonctionne sous overleaf, sinon CLI et tant pis/mieux
%\printbibliography

### 2021-05-05 6-ModelPresentation.tex
Updates from Overleaf

detailed  presentation  of  a  model,including justifications for design decisions

>>>>

% detailed  presentation of a model, including justifications for design decisions

Figure \ref{fig:MultilevelArchitecture} shows the overview of the multivel architecture designed to capture the two use cases described in Process Challenge.

% Expliquer que le use case XSure ne nécessitait pas l'extension de metamodèle requise pour le usecase Acme Software Developement Process

\subsection{Base metamodel for the Process Challenge}

\begin{figure*}
 \centering
    % \includegraphics[width=1.0 \columnwidth]{Figures/Metamodel.pdf}
    \includegraphics[width=1.0 \textwidth]{Figures/Metamodel.pdf}
    \caption{Process management base metamodel}
    \label{fig:BaseMetamodel}
\end{figure*}

\subsection{The XSure insurance domain}

The use case presented in this section is straightforward implementable while instantiating base metamodel presented in figure \ref{fig:BaseMetamodel}.

% Passer rapidement sur ce cas pour illustrer le metamodèle décrit plus haut

% We will illustrate the approach...

\subsection{The Acme software development process}

\subsection{Openflexo tooling}

% Expliquer l'outillage construit et comment il marche

### 2021-05-05 8-Discussion.tex

discussing choices  made, pointing out potential compromises/deficiencies

>>>>

discussing choices  made (ex : héritage vs attr), pointing out potential compromises/deficiencies
jc, fabien ; 
pas d'explicitation de niveaux de « concrétude » : conséquences ? facile de tracer des liens entre les niveaux ; difficile d'avoir le niveau ; 
outil adaptable, niveau d'abstraction, on fournit une solution + l'outil pour exécuter le processus ; réutilisabilité des modèles ; 
\todo{on pourrait aussi répondre ici aux 3 questions posées explicitement (copiées dansl'intro pour le moment)}

difficulctés/facilités
points saillants :  outillage "gratuit" ;

Although our tool was not designed with a focus on multi-level modelling, we were able to propose a fully working solution.

Our approach is level-blind, therefore it is not easy to quickly retrieve the abstraction level of a concept.
